### 2015-10-26 vmcai-2016-tex/abstract.tex
Added in some of the changes suggested by VMCAI reviewers.

A recent trend in the analysis of object-oriented programs is the
modeling of references as sets of guarded values, enabling multiple
heap shapes to be represented in a single state.  A fundamental
problem with using these guarded value sets is the inability to
generate test inputs in a manner similar to symbolic execution based
analyses.
%is the creation of test inputs for
%program analyses that accept symbolic reference input
%parameters.
Although several solutions have been proposed, none have been proven
to be sound and complete with respect to the heap properties provable
by generalized symbolic execution (GSE). This work presents a method for initializing input references
in a symbolic input heap using guarded value sets that exactly
preserves GSE semantics. A correctness proof for the initialization
scheme is provided with a proof-of-concept implementation. Results from an empirical evaluation on a standard set of \gsetxt{} benchmarks show an increase in the
size and number of analyzed heaps over existing GSE
representations. The initialization technique can be used to ensure
that guarded value set based symbolic execution engines operate in a
provably correct manner with regards to symbolic references as well as
provide the ability to generate concrete heaps that serve as test
inputs to the program.

>>>>

A recent trend in the analysis of object-oriented programs is the
modeling of references as sets of guarded values, enabling multiple
heap shapes to be represented in a single state.  A fundamental
problem with using these guarded value sets is the inability to
generate test inputs in a manner similar to symbolic execution based
analyses.
%is the creation of test inputs for
%program analyses that accept symbolic reference input
%parameters.
Although several solutions have been proposed, none have been proven
to be sound and complete with respect to the heap properties provable
by generalized symbolic execution (GSE). This work presents a method for initializing input references
in a symbolic input heap using guarded value sets that exactly
preserves GSE semantics. A correctness proof for the initialization
scheme is provided with a proof-of-concept implementation. Results from an empirical evaluation on a common set of \gsetxt{} data structure benchmarks show an increase in the
size and number of analyzed heaps over existing GSE
representations. The initialization technique can be used to ensure
that guarded value set based symbolic execution engines operate in a
provably correct manner with regards to symbolic references as well as
provide the ability to generate concrete heaps that serve as test
inputs to the program.

### 2015-10-26 vmcai-2016-tex/lazy.tex
Added in some of the changes suggested by VMCAI reviewers.

\section{GSE}
\label{app:gse}
GSE semantics are defined here to give insight to the new symbolic initialization approach and support the proof that the new approach preserves GSE behaviors. GSE and its variants have the same non-deterministic choice given a reference to an uninitialized object; that reference can point to null, a new instance of an object with the correct type, or to an object of the same type that has been instantiated previously by GSE \cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. The objects instantiated for new instances are referred to as the \emph{input heap}. Only these objects comprise the potential alias set when GSE encounters references to uninitialized objects. In general, the GSE search space branches at uninitialized objects, and the number of branches depends on the size of the input heap.

@@

How the lazy
initialization is used is defined in \figref{fig:lazy} with the $\rgse$ relation collecting all the rules into a single relation on states. This relation is used later by the proof. GSE initialization takes place on the field-access rule in \figref{fig:lazy},
using the $\rightarrow_I^*$ relation from \figref{fig:lazyInit}, to ensure the accessed field is
instantiated. Initialization in GSE never
happens for more than one object on any use of $\rightarrow_I^*$:
the set $\Lambda$ is either empty or contains exactly one location. This property is an artifact of how GSE case spits when it instantiates: each choice is a new unique heap. This changes in the next section with the new symbolic initialization that collects all the choices into a single heap using guarded value sets.

>>>>

\section{GSE}
\label{app:gse}
This section introduces \gsetxt\ semantics on which \symtxt\ builds. GSE and its variants have the same non-deterministic choice given a reference to an uninitialized object; that reference can point to null, a new instance of an object with the correct type, or to an object of the same type that has been instantiated previously by GSE \cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. The objects instantiated for new instances are referred to as the \emph{input heap}. Only these objects comprise the potential alias set when GSE encounters references to uninitialized objects. In general, the GSE search space branches at uninitialized objects, and the number of branches depends on the size of the input heap. The function
$\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
\{\lp\phi\ \cfgnt{l}\rp\ ...\}$ returns constraint-location
pairs where the field $\cfgnt{f}$ is uninitialized.

\[
\begin{array}{rcl}
\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
\end{array}
\]

@@

How the lazy
initialization is used is defined in \figref{fig:lazy} with the $\rgse$ relation collecting all the rules into a single relation on states. This relation is used later by the proof. GSE initialization takes place on the field-access rule in \figref{fig:lazy},
using the $\rightarrow_I^*$ relation from \figref{fig:lazyInit}, to ensure the accessed field is
instantiated. Initialization in GSE never
happens for more than one object on any use of $\rightarrow_I^*$:
the set $\Lambda$ is either empty or contains exactly one location. This property is an artifact of how GSE case splits when it instantiates: each choice is a new unique heap. This changes in the next section with the new symbolic initialization that collects all the choices into a single heap using guarded value sets.
